Output Summary

### 2020-11-20 03-post-process/output-plots.Rmd
Output plots: create fit plots for hydro survival data

```{r survival-data-fits, fig.width = 3, fig.height = 6}
par(mfcol = c(4,1), oma = c(1.5,1.5,0,0))

plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "(Nat) Summer Tagging to LGD")
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "(Nat) Fall Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = "(Nat) Spring Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

>>>>

```{r survival-data-fits, fig.width = 5, fig.height = 6}
par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))

plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "(Nat) Summer Tagging to LGD")
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "(Nat) Fall Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = "(Nat) Spring Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = "(Nat) LGD to BON")
plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = "(Hat) LGD to BON")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```
